\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling

### 2013-09-12 jss/article.tex
fixes

This package will be useful for frequentists and Bayesians alike. Bayesians are able to use the package to see results for a non-informative reference prior before and after constructing their own Bayesian hierarchical model. Frequentists will have a procedure that meets or exceeds their confidence specification and repeated sampling.

@@

Each indicator has the independent and identically distributed (\emph{iid}) Bernoulli($p_{cov, j}$) distribution, where $p_{cov, j}$ is the true coverage probability for the $j$-th group depending on specific values of $A$ and $\beta$.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> pcv <- coverage(p, nsim = 1000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h] 
\begin{center}
\includegraphics[width = 3.5in]{hospital2.png}
\caption{Coverage plot via frequency method checking for 31 hospitals}
\label{fig:hospitalcoverage}
\end{center}
\end{figure}

@@

The frequency method checking, assuming the model is correct, generates new pseudo-data from our assumed model. It starts by fixing the hyper-parameter values at their estimates ($\hat{A}$ and $\hat{\beta}_0$ in this example) unless these are specified. We then simulate ``true'' $\theta_j$ for each group $j$ and re-fit the model 1,000 times to estimate the coverage probabilities of our procedure.

\begin{CodeChunk}
\begin{CodeInput}
R> gcv <- coverage(g, nsim = 1000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h] 
\begin{center}
\includegraphics[width = 3.5in]{school2.png}
\caption{Coverage plot via frequency method checking for 8 schools}
\label{fig:schoolcoverage}
\end{center}
\end{figure}

@@

The 95\% interval plot shows the range of true batting average for each player, which clarifies the regression toward the mean (RTTM) within two groups. The 10th, 14th, and 15th players, for example, are outfielders but their observed batting averages are far lower than the first five outfielders. It can be due to their bad luck because their observed batting averages are close to their lower bounds of interval estimates (left tail area). RTTM suggests that their batting averages will shrink towards the expected prior mean of outfielders (0.310) in the long run.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> bcv <- coverage(b, nsim = 1000) 
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 3.5in]{baseball2.png}
\caption{Coverage plot via frequency method checking for 18 players}
\label{fig:baseball2}
\end{center}
\end{figure}

@@

In addition to the built in ``frequency method checking'' procedure the package can be used to undergo ``model checking''. For example, in the Gaussian model, the point estimates of $A$ and $\beta$ from the package are substituted into the marginal distribution in (\ref{normalmarginal}). And then we can check whether this maginal distribution explains the data better than the observed data distribution in (\ref{normalobs}). If better, e.g. in terms of data variation, we can benefit from the two-level hierarchical modeling on the dataset considered.

>>>>

This package will be useful for frequentists and Bayesians alike. Bayesians are able to use the package to see results for a non-informative reference prior before and after constructing their own Bayesian hierarchical model and frequentists will have a procedure with good repeated sampling properties.

@@

Each indicator has an independent and identically distributed (\emph{iid}) Bernoulli($p_{cov, j}$) distribution, where $p_{cov, j}$ is the true coverage probability for the $j$-th group depending on specific values of $A$ and $\beta$. 
%For reference, even if we sample $L$ datasets per one parameter set, $L\cdot N_{sim}$ indicators $I^{(i, l)}_{j}, i = 1, \ldots, N_{sim}, l = 1, \ldots, L$, have still $iid$ Bernoulli($p_{cov, j}$) distribution.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> pcv <- coverage(p, nsim = 1000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h] 
\begin{center}
\includegraphics[width = 3in]{hospital2.png}
\caption{Coverage plot via frequency method checking for 31 hospitals}
\label{fig:hospitalcoverage}
\end{center}
\end{figure}

@@

The frequency method checking, assuming the model is correct, generates new pseudo-data from our assumed model. Unless otherwise specified, the procedure fixes the hyper-parameter values at their estimates ($\hat{A}$ and $\hat{\beta}_0$ in this example) and then simulates ``true'' $\theta_j$ for each group $j$. The model is then estimated and this is repeated an \code{nsim} number of times to estimate the coverage probabilities of the procedure.

\begin{CodeChunk}
\begin{CodeInput}
R> gcv <- coverage(g, nsim = 1000)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h] 
\begin{center}
\includegraphics[width = 3in]{school2.png}
\caption{Coverage plot via frequency method checking for 8 schools}
\label{fig:schoolcoverage}
\end{center}
\end{figure}

@@

The 95\% interval plot shows the range of true batting average for each player, which clarifies the regression toward the mean (RTTM) within two groups. The 10th, 14th, and 15th players, for example, are outfielders but their observed batting averages are far lower than the first five outfielders. This can likely be attributed to their bad luck because their observed batting averages are close to the lower bounds of their interval estimates. RTTM suggests that their batting averages will shrink towards the expected prior mean of outfielders (0.310) in the long run.

@@

\begin{CodeChunk}
\begin{CodeInput}
R> bcv <- coverage(b, nsim = 1000) 
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 3in]{baseball2.png}
\caption{Coverage plot via frequency method checking for 18 players}
\label{fig:baseball2}
\end{center}
\end{figure}

@@

In addition to the built in ``frequency method checking'' procedure the package can be used to undergo ``model checking''. For example, in the Gaussian hierarchical model, the assumed marginal distribution of the data is given in (\ref{normalmarginal}). By substituting the point estimates of $A$ and $\beta$ from the package into this marginal distribution a test can be constructed to see whether the data follow the marginal distribution suggested by the hierarchical model.
